A Case Study on Abstractions to Converge High-Throughput and High-Performance Computing

### 2017-03-21 introduction.tex
Fix bibliography, the joy of latex

The Large Hadron Collider (LHC) was created to explore the fundamental
properties of matter for the next decades.  Since LHC start-up in 2009,
multiple experiments  at LHC have collected and distributed hundreds of
petabytes of data worldwide to hundreds of computer centers.
Thousands of physicists analyze petascale data volumes daily.
One of the LHC experiments, the ATLAS~\cite{Aad:2008}, utilizes the Production
and Distributed Analysis (PanDA) workload management system~\cite{Maeno2011}
(WMS) for distributed data processing and analysis. The ATLAS Computing
model~\cite{Atlas2005} is based on a Grid paradigm~\cite{Foster:1998}, with
multilevel, hierarchically distributed computing and storage resources. PanDA
has been developed to meet growing ATLAS production and analysis requirements
for a data-driven workload management system capable of operating at LHC data
processing scale.

>>>>

The Large Hadron Collider (LHC) was created to explore the fundamental
properties of matter for the next decades.  Since LHC start-up in 2009, multiple
experiments  at LHC have collected and distributed hundreds of petabytes of data
worldwide to hundreds of computer centers. Thousands of physicists analyze
petascale data volumes daily. One of the LHC experiments, the
ATLAS~\cite{Aad:2008}, utilizes the Production and Distributed Analysis (PanDA)
workload management system~\cite{Maeno2011} (WMS) for distributed data
processing and analysis. The ATLAS Computing model~\cite{jones2008atlas} is
based on a Grid paradigm~\cite{foster2003grid}, with multilevel, hierarchically
distributed computing and storage resources. PanDA has been developed to meet
growing ATLAS production and analysis requirements for a data-driven workload
management system capable of operating at LHC data processing scale.
